Standard Deviation Outcome Change - DEVELOPMENT

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Added function for producing marginal distribution plots for a single year (baseline vs intervention). Cleaned up some of the standard_deviation_change_SF12.Rmd script also

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
```

@@

@@

```{r}
# get just one year
b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
b.2030 <- base %>% filter(time == 2030, SF_12 != -8.0)
i.2030 <- int %>% filter(time == 2030, SF_12 != -8.0)
```

```{r}
# get just the SF12 columns
#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
```

```{r}
# combine before we plot
b.2030$scen <- 'baseline'
i.2030$scen <- 'energyDownlift'

#combined <- merge(b.2030, i.2030, by = 'pidp')
combined <- rbind(b.2030, i.2030)

# now merge with initial
merged <- merge(b.2020, combined, by = 'pidp')
```

```{r}
p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
  geom_point(alpha = 0.6, size=0.1) +
  geom_smooth() +
  theme(legend.position = c(0.15, 0.9))

p1 <- ggMarginal(p, type='density', groupColour = TRUE)
p1

ggsave(filename = 'scatter_marg_dens_energy.png',
       plot = p1,
       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
```

```{r}
p2 <- ggMarginal(p, type='histogram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p2

@@

```{r}
p3 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p3
ggsave(filename = 'scatter_marg_densigram_energy.png',
       plot = p3,
       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
```

>>>>

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
source('Minos/minos/utils_outcome_vis.R')
```

@@

## Workings

@@

```{r}
# get just one year
#b.2020 <- base %>% filter(time == 2020, SF_12 != -8.0)
b.2030 <- base %>% filter(time == 2030, SF_12 != -8.0)
i.2030 <- int %>% filter(time == 2030, SF_12 != -8.0)
```

```{r}
# get just the SF12 columns
b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(baseline = SF_12)
i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(intervention = SF_12)
#b.2020 <- b.2020 %>% select(pidp, SF_12) %>% rename(initial = SF_12)
#b.2030 <- b.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
#i.2030 <- i.2030 %>% select(pidp, SF_12) %>% rename(end = SF_12)
```

```{r}
# combine before we plot
#b.2030$scen <- 'baseline'
#i.2030$scen <- 'energyDownlift'

combined <- merge(b.2030, i.2030, by = 'pidp')
#combined <- rbind(b.2030, i.2030)

# now merge with initial
#merged <- merge(b.2020, combined, by = 'pidp')
```

```{r}
p <- ggplot(data = combined, aes(x = baseline, y = intervention)) +
  geom_point(alpha = 0.6, size=0.1) +
  geom_smooth() +
  theme(legend.position = c(0.15, 0.9))

p1 <- ggMarginal(p, type='density')
p1

#ggsave(filename = 'scatter_marg_dens_energy.png',
#       plot = p1,
#       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')

#p5 <- SF12_marg_dist_densigram_plot_oneyear(base,
#                                           int,
#                                           int.name = 'Energy Downlift',
#                                           target.year = 2030)
```

```{r}
p2 <- ggMarginal(p, type='histogram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p2

@@

```{r}
p3 <- ggMarginal(p, type='densigram', xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p3
ggsave(filename = 'scatter_marg_densigram_energy.png',
       plot = p3,
       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
```

## Testing

```{r}
out.path <- 'Minos/output/default_config/'
# Test out the new function above
base <- read_singular_local_out(out.path, 'baseline')
livWage <- read_singular_local_out(out.path, 'livingWageIntervention')
energy <- read_singular_local_out(out.path, 'energyDownlift')
poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
```

### Initial -> 2030

```{r}
p.livWage <- SF12_marg_dist_densigram_plot(base, 
                                        livWage, 
                                        int.name = 'Living Wage',
                                        target.year = 2030,
                                        save=TRUE)
p.energy <- SF12_marg_dist_densigram_plot(base, 
                                        energy, 
                                        int.name = 'Energy Downlift',
                                        target.year = 2030,
                                        save=TRUE)
p.poverty <- SF12_marg_dist_densigram_plot(base, 
                                        poverty, 
                                        int.name = 'Poverty Child Uplift',
                                        target.year = 2030,
                                        save=TRUE)
p.allchild <- SF12_marg_dist_densigram_plot(base, 
                                        allchild, 
                                        int.name = 'Child Uplift',
                                        target.year = 2030,
                                        save=TRUE)
```

### Single Year

```{r}
p2.livWage <- SF12_marg_dist_densigram_plot_oneyear(base, 
                                        livWage,
                                        int.name = 'Living Wage',
                                        target.year = 2030,
                                        save=TRUE)
p2.energy <- SF12_marg_dist_densigram_plot_oneyear(base, 
                                        energy, 
                                        int.name = 'Energy Downlift',
                                        target.year = 2030,
                                        save=TRUE)
p2.poverty <- SF12_marg_dist_densigram_plot_oneyear(base, 
                                        poverty, 
                                        int.name = 'Poverty Child Uplift',
                                        target.year = 2030,
                                        save=TRUE)
p2.allchild <- SF12_marg_dist_densigram_plot_oneyear(base, 
                                        allchild, 
                                        int.name = 'Child Uplift',
                                        target.year = 2030,
                                        save=TRUE)
```
